Apache Flink\texttrademark: Unified Stream and Batch Processing \\ in a Single Engine

### 2015-11-26 streaming.tex
Merge with Paris' changes

As an example consider a stream wordNums containing words and an associated number for each word. We can use the partitionable  OperatorState in a stateful map function to compute a rolling average number seen per word by marking a sum and count per word as explicit states along with their updates:

\begin{lstlisting}[language=Java]
wordNums.keyBy(0).map(new StatefulAverage())

public class StatefulAverage implements RichMapFunction<Long, Double> {
    private OperatorState<Long> sum;
    private OperatorState<Long> count;

    public Double reduce(Tuple2<String,Long> num) {
        count.update(count.value() + 1);
        sum.update(sum.value() + num.f1)
        return new Tuple2(num.f0, (double) sum.value()/count.value());
    }
...
}
\end{lstlisting}

>>>>

As a simple example consider a map operator that computes a continuous average for a given stocks price. For this we need to keep a state with the current count and total sum for each stock in order to compute the average:

\begin{lstlisting}[language=Scala]
val priceStream: DataStream[(String,Double)] = ...
 
val avgPerStock : DataStream[(String, Double)] = source.keyBy(0).mapWithState(
    (in, state: Option[(Int, Double)]) => {
		val (count, sum) = state.getOrElse((0,0.0))
		val newState = (count + 1, sum + in._2)
		((in._1, newState._2/newState._1), newState)
	}
\end{lstlisting}
